% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}
\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Set your information here
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% name
\def\name{Sam Lewallen}
% email
\def\email{sam.lewallen@gmail.com}
% email
\def\url{https://lewallen.github.io/}
% address
\def\address{
Center for Brain Science \\
Harvard University \\
52 Oxford St \\
Cambridge, MA 02138  
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Line skip macros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\lsk{\\[.2em]}
\def\lskk{\\[.3em]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {neuroscience, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  %  right=.60in,
  %  bottom=.60in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\def\urltilda{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}
\newcommand{\urltilde}{\kern -.15em\lower .7ex\hbox{~}\kern .04em}
% \renewcommand{\baselinestretch}{1}

\def\tightlist{}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PERSONAL INFO:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Place name at left
{\huge \name}
\hfill% move it to the right
\begin{tabular}[t]{l@{}}
\textit{\today}
\end{tabular}
\vspace{0.4in}

\begin{minipage}{0.45\linewidth}
\address
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Email: & \href{mailto:\email}{\tt \email} \\
    Homepage: & \href{\url}{\tt \url} \\
  \end{tabular}
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education and employment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \textbf{Swartz Fellow} \lsk
Center for Brain Science, Harvard University \lsk
\textit{2018 - Present} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Postdoctoral Research Fellow} \lsk
Princeton Neuroscience Institute \lsk
Advisor: David Tank \lsk
\textit{2014 - 2018} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Methods in Computational Neuroscience summer school} \lsk
MBL, Woods Hole, MA \lsk
\textit{2013} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Ph.D., Mathematics} \lsk
Princeton University \lsk
Advisor: Zolt\'{a}n Szab\'{o} \lsk
Thesis title: \textit{Floerg\aa sbord}. (General subject matter: Low-dimensional topology, topological quantum field theory) \lsk
\textit{2008 - 2014} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{B.A., Mathematics} \lsk
Harvard University \lsk
Graduated with Highest Honors \lsk
\textit{2004 - 2008}
  \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item Probing variability in a cognitive map using manifold inference from
neural dynamics. \lsk
Ryan J Low*, \textbf{Sam Lewallen}*, Dmitriy Aronov, Rhino Nevers, David W Tank
(2018). \emph{bioRxiv}. \\

\item A map-like micro-organization of grid cells in the medial entorhinal
cortex. \lsk
Yi Gu, \textbf{Sam Lewallen}, Amina A Kinkhabwala, Cristina Domnisoru, Kijung Yoon, Jeffrey L Gauthier, Ila R Fiete, David W Tank (2018). \emph{Cell}. \\

\item Grid cell responses in 1D environments assessed as slices through a 2D
lattice. \lsk
KiJung Yoon*, \textbf{Sam Lewallen}*, Amina A Kinkhabwala, David W Tank, Ila R
Fiete (2016). \emph{Neuron}. \\

\item Stimulus-dependent correlations in threshold-crossing spiking neurons.  \lsk
Yoram Burak, \textbf{Sam Lewallen}, Haim Sompolinsky (2009). \emph{Neural
Computation}. \\

\item (1,1) L-space knots. \lsk
Joshua Evan Greene, \textbf{Sam Lewallen}, Faramarz Vafaee** (2018).
\emph{Compositio Mathematica}. \\

\item Strong L-spaces and left orderability. \lsk
Adam Simon Levine, \textbf{Sam Lewallen}** (2012). \emph{Mathematical Research
Letters}. \\

$*$ Joint first authors \lsk
$**$ Authors in alphabetical order

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Awards and fellowships}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item NSF Nordic Fellowship, 2011 
\item NSF Graduate Research Fellowship, 2008-2011 
\item Centennial Fellowship, 2008-2011 (awarded to top few incoming Phd students by Princeton math department) 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Other research experiences in neuroscience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item Independent undergraduate research project advised by Haim Sompolinsky, Harvard University 

\textit{Summer, 2007}

\item Undergraduate research assistant with  Maria Geffen and Marcello Magnasco, Rockefeller University

\textit{Summer, 2006}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip

\end{document}


% REMOVED:

\section*{List of research experiences in neuroscience}

\begin{itemize}
\item \Summer, 2006

Worked as assistant in the lab of Marcello Magnasco and Maria Geffen at Rockefeller University.  Wrote data acquisition software, helped set up lab for auditory cortex recordings in mice  

\item  Summer, 2007   

Worked on independent theoretical summer project guided by Haim Sompolinksy, at Harvard University 

\item  Spring, 2012 - Present   

Working on grid cell modeling and data analysis with the Tank lab at Princeton University  

\end{itemize}

\section*{Neuroscience courses}

\begin{itemize}
\item Harvard: Introduction to Neuroscience (John Dowling), Systems Neuroscience (Florian Engert), Computational Neuroscience (Haim Sompolinsky)

\item Princeton: Attended the first semester of the overview  course required for all first year graduate students in neuroscience (Princeton faculty)

\end{itemize}



\item Swartz Meeting, University of Washington, Summer 2014
%\item UT Austin, Spring 2013, Fiete group meeting
\item Harvard University, Spring 2013, Neurolunch seminar
\item UC Davis, Spring 2013, computational neuroscience seminar
\item Brandeis University, Fall 2012, Topology seminar
\item UCLA, Spring 2011, Topology seminar
\item Caltech, Spring 2011, Topology seminar
\item Michigan State Unversity, Fall 2010, Topology seminar
\item Indiana University, Bloomington, Fall 2010, Topology seminar
\item MSRI, Berkeley, Spring 2009, Knot homologies program seminar



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Computer competencies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item MATLAB, Python, Mathematica, C++

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Invited/external talks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item To be added.

\end{itemize}







